A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-16 08_MetaAnalysis_Emerson.Rmd
more explaination

```{r compare2PowderyMildewMDM}

@@

>>>>

One aspect we would like to consider is how the results of this meta-analysis compares to how the PowderyMildewMBM estimates the effect of fungicide applications on grain yields.
Below we create a data frame of the mitigation factors for each spray scenario so we can compare them to the outcomes of the meta-analysis.
```{r compare2PowderyMildewMDM}

@@

```
To to a better comparison I need to know how the mitigation factor is calculated with the estimated yields
